Web data extraction through named entity labeling

### 2018-11-29 tex/article.tex
New article.

\documentclass[sigconf]{acmart}
\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers
\setcopyright{none}

@@

\title{Named Entity Recognition on HTML as a web data extraction subtask}

\author{João Mateus de Freitas Veneroso}
\affiliation{%
  \institution{Universidade Federal de Minas Gerais}
  \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
  \city{Belo Horizonte}
  \state{MG}
  \postcode{31270-901}
  \country{Brazil}}
\email{jmfveneroso@gmail.com}

\author{Berthier Ribeiro-Neto}
\affiliation{%
  \institution{Universidade Federal de Minas Gerais}
  \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
  \city{Belo Horizonte}
  \state{MG}
  \postcode{31270-901}
  \country{Brazil}}
\email{berthier@dcc.ufmg.br}
\email{berthier@google.com}

@@

Web data extraction (WDE) methods often rely on hand-coded rules to 
identify and extract data from web pages. These methods 
may be suited to extract information from single websites, but
they usually perform poorly on extraction tasks across different 
websites or different application domains. Statistical methods
are more flexible in this regard. In this paper, we investigate
different approaches to Named Entity Recognition (NER) on HTML, an
essential substask in statistical models of web data extraction.
Webpages can be very different from plain text due to their 
semistructured nature, so we introduced a novel dataset that focuses
on researcher name extraction from faculty listings from numerous
university websites to evaluate different models in the 
NER on HTML task. We found that neural network
architectures with a Conditional Random Fields output layer and
neural character representations are able to achieve an F1-score
of 0.8867 with no inputs besides word embeddings. These NER models 
can be part of a flexible and effective approach to WDE that does not
rely on gazetteers, regular expressions or any hand-coded rules.

@@

Web data extraction (WDE) is the task of automatically extracting structured information
from unstructured or semi-structured web documents. The input usually consists of
web documents containing a number of predetermined entities organized in a similar 
manner and the information extraction task consists of identifying these entities
and organizing them according to a template. In this context, named entity recognition
(NER) is a subtask that aims to detect named entities in the text and classify them into 
predetermined categories such as person names, locations or organizations.

HTML documents most often lie in between the structured / unstructured data paradigm.
DOM hierarchy, element disposition, class names, and other features related to 
the document structure and indirectly associated with the data itself can be valuable 
information on the task of identifying entities and determining relationships. Yet we 
cannot expect these features to be completely constrained by an underlying pattern. 
Organization patterns tend to follow some guidelines but are in no way subject to 
strict rules. That is why classical information extraction systems such as automatic
wrapper generators usually do not translate well across different websites.

Most existing web data extraction methods are tailored to extract data from a single
web page \cite{Crescenzi2001, Arasu2003, Freitag1998, Califf1999, Soderland1999,
Kushmerick2000, Hsu1998, Muslea1999}, producing different compromises between efficacy
and degree of human supervision. More recent unsupervised approaches proposed to
tackle the problem of data extraction for whole application domains \cite{Zhu2005, Zhu2006, 
Abdessalem2010, Furche2012, Furche2012a}. Unsupervised WDE methods usually operate in at
least two steps: record segmentation and attribute labelling. Record segmentation
is essentially clustering visually and structurally similar web page regions and 
identifying repeating data records. Attribute labelling is the task of identifying
attributes in data records. Doing any of these tasks well can help performing the 
other task, since patterns that are present in some data records can help identifying 
attributes in other data records. And by properly identifying attributes, we are better 
able to determine the boundaries of data records and segment them with increased accuracy.

In recent years, we saw an astonishing progress in Natural Language Processing.
However, despite WDE being a closely related field of research,
many tools rely on heuristics or hand-coded rules to perform record segmentation,
and many methods resort to regular expressions or gazetteer matching to perform attribute
labelling. While these approaches can be sufficient to extract information from webpages
with similar templates and identifying attributes with distinct formats like prices and
dates, we still lack a sufficiently flexible and intelligent approach to handle more complicated cases.
Even when extracting data from web documents only, data records may contain pure text with 
relevant named entities. Also, many WDE algorithms can effectively exploit the semi-
structure of web documents, but when a method relies too much on structural features, it
often produces poor generalization on cross website extraction tasks. Contrastingly, we 
understand that statistical based approaches can be much more flexible.

In this paper, we investigate the attribute labelling task in WDE with a named entity 
recognition framework. Recently proposed neural architectures have achieved exciting results 
on the NER task on plain text \cite{Huang2015, Lample2016, Ma2016} while requiring almost 
no feature engineering or gazetteers. NER on HTML poses a different type of challenge, 
because web pages are often very different from plain text. Named entities may be present 
inside tables, lists, graphs or other types of visual elements that provide
little to no textual information that could give hints about the semantic category of 
a word. However we show that we can get exceptional performance even with this limitation
and small training sets.

By reliably detecting named entities, we can improve the performance of existing WDE 
approaches or even construct a full machine learning based tool to tackle domain wide
extraction with great flexibility. To test different NER approaches from the perspective 
of web data extraction,
we explored the task of person names extraction from university faculty listings.
Researcher affiliation is often missing from many entries in public databases 
and the display of information varies significantly between different university 
websites, so this task can provide a good measure of the expected performance and
data need for other web data extraction tasks.

@@

In the last 20 years, the astonishing growth of public information in the web has 
led to the development of a number of different approaches to the problem of web 
information extraction. Traditionally, the task was solved by designing special purpose
programs called wrappers to recognize relevant data and store records in a structured
format. These early tools varied wildly relative to their degree of automation.

@@

To automate the task of web data extraction completely some approaches,
such as Road Runner \cite{Crescenzi2001}, removed entirely the need for data examples.
Road Runner parses documents belonging to a same class (e.g. books on Amazon) and 
generates wrappers based on their similarities and differences, yielding comparable results 
to those obtained by wrapper induction methods. However like previous approaches, it was 
unsuited for cross site extraction tasks because the learned rules were not general enough.

@@

In 2008, Sarawagi \cite{Sarawagi2008} produced a survey that classified wrappers into
rule-based methods, statistical methods and hybrid models, bringing together 
the fields of named entity recognition, relationship extraction and information extraction. 
The rule based methods encompass most of the 
previous models. The statistical methods convert the extraction task into a token labeling 
task, identifying the target entities through the assignment of labels as in a typical 
Named Entity Recognition task. Traditionally, Hidden Markov Models \cite{Leek1997, Freitag1999}, 
Linear Chain Conditional Random Fields \cite{Lafferty2001}, and Maximum Entropy Taggers 
\cite{McCallum2000} have been the usual choice for linear sequence tagging models.
More recently, with the advancement of Natural Language Processing and Deep Learning, 
neural models outperformed previous NER methods. Huang et. al. \cite{Huang2015} introduced the 
bidirectional Long Short-Term Memory (LSTM) model with a Conditional Random Field (CRF) output layer
for NER. Lample et. al. \cite{Lample2016} incorporated Convolutional Neural Network based character representations 
on top of the architecture. And Ma and Hovy \cite{Ma2016} introduced
LSTM based character representations. Both obtaining improvements with systems that are less reliant
on feature engineering.

@@

Most data extraction systems focus on extracting information from single websites
and are therefore unsuited for cross website extraction tasks. Even unsupervised
approaches that are domain independent, such as RoadRunner \cite{Crescenzi2001} 
and EXALG \cite{Arasu2003} only work well for extracting data from pages generated 
from the same template. A statistical approach to unsupervised domain 
independent web data extraction was described by Zhu et al \cite{Zhu2005}. The 2D CRF 
model takes a web page segmented into data blocks and employs a two dimensional conditional 
random field model to perform attribute labelling. The model was further improved in 
\cite{Zhu2006} to model record segmentation and attribute labelling as a joint task.
Some of the limitations of early unsupervised methods 
were also tackled by ObjectRunner \cite{Abdessalem2010} and AMBER \cite{Furche2012}. 
These methods work by annotating webpages automatically with regular expressions, gazetteers and 
knowledge bases. They can rectify low quality annotations and even improve the annotators
by exploring regular structures in the DOM during the record segmentation phase.

Web data extraction methods have undoubtedly improved extraordinarily, but
as pointed by Schulz et al. \cite{Schulz2016}, it is difficult to compare the results 
achieved by competing tools, and many seem to rely excessively on certain heuristics.
In that regard, the impressive advancements in NLP may provide for more robust and
flexible extraction tools.

@@

Most web data extraction systems rely on hand crafted rules or gazetteers to perform
attribute annotation. Machine learning approaches to NER can improve annotations of 
more complex entities and even manage entity detection without resorting to a gazetteer.
We explored multiple approaches to the Named Entity Recognition problem in the context 
of a web information extraction task. First, we introduce two traditional approaches, 
namely: Hidden Markov Models and Linear Chain Conditional Random Fields. Then
we explore neural network architectures.

@@

Since $ P(X) $ is the same for all label sequences $ Y $, we can simply maximize
$ P(X|Y) P(Y) $.

A HMM makes two assumptions. First, the probability of being in a given state depends 
only on a fixed number of previous states. That is 
$ P(y_i|y_{i-1}x_{i-1}, y_{i-2}x_{i-2}, ..., y_1x_1) = P(y_i|y_{i-1}, y_{i-2},..., y_{i-k}) $. 
In fact, we can get much better results on the NER task by looking at trigrams
or quadrigrams ($ k = 2 $ or $ k = 3 $) instead of bigrams as a regular HMM. 
Some label assignments are highly improbable, such as single token named entities 
separated by a common word, and these kinds of patterns can be caught by a higher order HMM.
Second, the probability of a word depends only on its assigned label 
$ P(x_i|y_{i-1}x_{i-1}, ..., y_1x_1) = P(x_i|y_i) $. With these assumptions, 
the probability $ P(Y|X) $ can be approximated by the expression:

@@

The probabilities can be calculated through maximum likelihood estimation from the relative
frequencies of labels and features in the corpus. The best sequence of labels can be computed 
with a variable state Viterbi approach \cite{Li2000}. However, as we increase $ k $, this computation 
becomes exponentially more expensive. The beam-search strategy may be employed for a faster 
search, but we found that for $ k \leq 4 $, the Viterbi algorithm is still viable.

HMM based taggers have been succesfully apllied in many NLP and WDE tasks 
\cite{Rabiner1990, Leek1997, Freitag2000}. They are incredibly fast to train and very 
interpretable, making them a good choice for a first approximation. However, these models 
are highly dependent on the right selection of features, what may outweigh the benefit of a 
small training cost.

@@

In the particular case of NER on HTML, there are useful features related to the HTML
structure that can be used to identify named entities. In a particular website, named
entities tend to occur inside the same HTML tags with the same CSS classes. This fact
can be used as an additional piece of evidence in the HMM tagger. However, if we train 
the HMM for a particular set of websites, and then we feed it with new websites, almost 
surely there will be small correlation between the HTML features estimated in the training 
set and the distribution of these features in the new websites, simply because websites 
use very different templates. Therefore, we propose to use a self training strategy to train 
these HTML features. This is only possible because the HMM can be trained very quickly. The 
self training strategy is implemented like this:

\begin{itemize}
\item Train the HMM with the training set without HTML features.
\item Compute labels for the new websites with the trained HMM.
\item Use these computed labels as a proxy for the actual labels in the 
new websites and estimate HTML feature frequencies only in the new websites.
\item Recompute the labels using the HTML features.
\end{itemize}

This adds very little overhead to the original model while improving precision and recall
modestly.

@@

which is a sum over all possible label assignments $ Y $. The partition function can be efficiently
and exactly calculated with the sum-product algorithm. Parameter estimation is usually done through 
negative log likelihood minimization. The function can be optimized with techniques suitable for other 
maximum entropy models such as L-BFGS \cite{Liu1989}. The most likely label sequences can be decoded 
with the Viterbi algorithm, as was the case on HMMs.

CRFs are more general than HMMs because the transitions from $ y_{t-1} $ to $ y_{t} $ can also depend 
on the vector of observations $ X $. This flexibility of feature functions allow for a wide range of
possibilities. Recently, CRFs have been succesfully employed as the output layer in complex neural 
architectures bringing improvements over models that classify labels independently.

\subsection{Neural Network Models}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{pics/rnn_network}
  \caption{RNN for NER}
  \label{fig:rnn_network}
\end{figure}

@@

Although RNNs are theoretically capable of learning long term dependencies, in practice 
it might be difficult. Long short term memory networks (LSTM) were introduced by Hochreiter 
and Schmidhuber \cite{Hochreiter1997} with this problem in mind and have been 
popularized since them. LSTM cell implementations vary slightly in the literature.
Our implementation has the following definition:

@@

In NER related tasks, both past and future words are important when deciding the
label at time $ t $, but a regular LSTM network only takes past features in consideration. 
A bidirectional LSTM solves this problem by stacking two regular LSTMs, and feeding
them with observations in opposite directions. The first LSTM receives the forward
states and the second LSTM receives the backward states. The hidden states from both 
networks can be concatenated at each time step to produce the output label. With this 
architecture, Bidirectional LSTMs have information from all input features in the sequence at 
any given timestep.

@@

The unaccented lowercase token was used as the key for the Glove-100 embedding lookup.
A gazetteer was constructed from a researcher list extracted from DBLP with 1.595.771
names. Table \ref{tab:gazetteer} shows the precision, recall and F1 score obtained with an
exact gazetteer matching strategy in each data file as a baseline.
Feature 2 represents an exact match of a sequence of tokens to any of the 1.595.771 
names, and feature 3 represents a partial match. Feature 4 is the rounded logarithm of 
the frequency of a token in the gazetteer, and feature 5 is the rounded logarithm of the frequency
of a token in a word corpus obtained through a random crawl in university websites.
Features 6 to 11 represent a simple regular expression match to an email, number, 
honorific, URL, capitalization and punctuation sign.

Feature 12 represents the HTML enclosing tag and its parent concatenated. Feature 13
represents all CSS classes concatenated. These features are not very useful in a general
sense, because every HTML document has a different format, so only because a named entity
occurs inside a given HTML tag in a document we cannot say it is more likely to be the case 
in other documents. However, these features can be trained with the self-training strategy 
for HMMs described in section \ref{sssec:self_training}. In all other models these features 
were ignored.

@@

Two experiments were conducted to evaluate the best models for named entity recognition
on HTML in the context of web data extraction. In the first experiment, we trained the NER models
using the entire training set (85 documents). In the second experiment, the training set was 
split into five non overlapping sets with 17 documents, and every model was trained
and tested once using each set, while the test data was kept unchanged. We wanted to verify empirically 
how the models behaved when training data is limited, since labelling NER datasets can be a
very time consuming effort.

@@

\bibliographystyle{unsrt}
\bibliography{bibfile}

>>>>

\documentclass{nle}

% \documentclass[sigconf]{acmart}
% \settopmatter{printacmref=false} % Removes citation information below abstract
% \renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
% \pagestyle{plain} % removes running headers
% \setcopyright{none}

@@

\title{Web data extraction through named entity labeling}

\author{João Mateus de Freitas Veneroso}
% \affiliation{%
%   \institution{Universidade Federal de Minas Gerais}
%   \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
%   \city{Belo Horizonte}
%   \state{MG}
%   \postcode{31270-901}
%   \country{Brazil}}
% \email{jmfveneroso@gmail.com}
% 
% \author{Berthier Ribeiro-Neto}
% \affiliation{%
%   \institution{Universidade Federal de Minas Gerais}
%   \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
%   \city{Belo Horizonte}
%   \state{MG}
%   \postcode{31270-901}
%   \country{Brazil}}
% \email{berthier@dcc.ufmg.br}
% \email{berthier@google.com}

@@

Web data extraction methods often rely on hand-coded rules to 
identify and extract data from web pages. These methods are usually
suited for extracting information from repeating templates inside
the same website, however they perform poorly on extraction 
tasks across different websites. Alternatively, statistical and 
machine-learning-based sequence labeling methods provide a more flexible 
approach to Web data extraction. HTML text is ocasionally very different 
from plain text because sentences can be too short to provide adequate 
context for conventional Named Entity Recognition methods to work 
properly. Also, the HTML structure can encode information that is not 
replicated in the text. Nonetheless, these limitations can be overcome by
adequate feature engineering, the use of pre-trained word 
embeddings and neural character representations. In this article, we 
evaluate the performance of different methods of named entity recognition 
on the task of Web data extraction. In particular, we introduce a novel 
dataset consisting of faculty listings from university webpages across
the world in multiple languages and test the NER models on the task of 
extracting researcher names from these listings. We found that a 
neural network architecture that combines a bidirectional LSTM with
a Conditional Random Fields output layer and LSTM-based character 
representations outperforms other methods on the researcher name 
extraction task, achieving an F1-score of 0.8867 with no feature engineering. 
With the addition of hand crafted features, the F1-score can be slightly 
improved to 0.8995 with another neural architecture that incorporates
CNN-based character representations.

@@

Web data extraction (WDE) is the task of automatically extracting structured 
information from unstructured or semi-structured Web documents. The input 
usually consists of Web documents containing a number of predetermined entities 
organized in a similar manner. The web data extraction task consists of 
identifying these entities and organizing them according to a template.

HTML documents most often lie in between the structured/unstructured 
data paradigm. DOM hierarchy, element disposition, CSS classes, and other 
features related to the document structure and indirectly associated with the 
data itself can be valuable information on the task of identifying
entities. Yet, we cannot expect these features to be completely constrained 
by an underlying pattern. Organization patterns tend to follow some guidelines 
but they are in no way subject to strict rules. That is why classical web data 
extraction systems such as automatic wrapper generators 
\cite{Kushmerick2000,Hsu1998,Muslea1999}
do not translate very well across different websites.

Most existing Web data extraction methods are tailored to extract data 
from a single Web page, producing different compromises between efficacy and 
degree of human supervision. Some unsupervised approaches proposed to tackle 
the problem of data extraction for whole application domains 
\cite{Zhu2005,Zhu2006,Abdessalem2010,Furche2012,Furche2012a}. Usually, 
unsupervised WDE methods work in two stages. In the record segmentation stage,
WDE systems seek to cluster visually and structurally similar web page regions 
and identify repeating data records, usually with heuristics and 
hand-coded rules. In the attribute labelling stage, WDE systems seek to identify 
the correct attributes on data records, many times resorting to regular expressions 
or gazetteer matching strategies. The outcome of each of these stages can aid one 
another. The inner patterns of data records can help identifying attributes in other 
data records. Also, by properly identifying data record attributes, it becomes 
easier to determine boundaries and perform record segmentation.

While unsupervised approaches can be sometimes adequate to extract information from 
webpages with similar templates, they usually fail on cross-website data extraction 
tasks. Also, more sophisticated approaches may be needed when we are not dealing
with easily distinguishable attributes such as prices and dates. In this regard, 
machine-learning-based sequence labeling methods can provide a more flexible 
approach that works regardless of website structure.

In recent years, we saw an amazing progress in the field of Natural Language Processing, 
particularly with the introduction of deep recurrent neural network architectures
for sequence labeling. However, despite web data extraction being a closely 
related field, there is a lack of extraction tools that make use of these recent 
advancements. The attribute labelling stage in web data extraction systems
is essentialy a Named Entity Recognition (NER) problem, the problem of 
detecting named entities in the text and classifying them into predetermined 
categories such as person names, locations, dates or organizations.

In many cases, such as when we are extracting researcher names from faculty listings,
detecting named entities is sufficient to solve the data extraction task. However, when we are
dealing with multi attribute data records or complex relationships, we may need to 
perform additional steps. Nevertheless, even in the latter cases, flexible NER methods 
are still desirable because, while many WDE algorithms can effectively exploit the 
semi-structured nature of web documents, too much reliance on structural webpage 
features often produce poor generalizations on cross website extraction. Also, 
data records may enclose plain text with relevant named entities.

In this paper, we investigate methods of named entity recognition for web data extraction.
Recently proposed neural architectures have achieved exciting results 
on the NER task in plain text while requiring almost 
no feature engineering or access to gazetteers \cite{Huang2015,Lample2016,Ma2016}. 
NER on HTML poses a slightly different type of challenge. Named entities may occur inside 
tables, lists, graphs or other types of visual elements that provide little to no textual 
information that could give hints about the semantic category of a word. Still, even 
with this limitation, we show that it is possible to obtain very good results with a 
relatively small training set.

By reliably detecting named entities on HTML, we can improve the performance of existing WDE 
approaches or even construct an end-to-end neural network architecture to tackle domain 
wide extraction with considerable flexibility. To test different NER approaches to
web data extraction, we explored the task of researcher name extraction from university 
faculty listings across the world, introducing a novel NER dataset.

Reliable researcher affiliation information is often missing from public researcher 
databases (especially in departments other than Computer Science). Also, the display of 
faculty information varies significantly between different university websites, so 
this task can provide a good measure of the expected performance and data need of
NER methods on other web data extraction tasks.

@@

In the last 20 years, the astonishing growth of public information in the web has 
led to the development of a number of different approaches to the problem of web 
data extraction. Traditionally, the task was solved by designing special purpose
programs called wrappers to recognize relevant data and store records in a structured
format. These early tools varied wildly relative to their degree of automation.

@@

To automate the task of web data extraction completely some approaches,
such as Road Runner \cite{Crescenzi2001}, removed entirely the need for data examples.
Road Runner parses documents belonging to a same class (e.g. books on Amazon) and 
generates wrappers based on their similarities and differences, yielding comparable results 
to those obtained by wrapper induction methods. However, like previous approaches, it was 
unsuited for cross site extraction tasks because the learned rules were not general enough.

@@

In 2008, Sarawagi \cite{Sarawagi2008} produced a survey that classified wrappers into
rule-based methods, statistical methods and hybrid models, bringing together 
the fields of named entity recognition, relationship extraction and information extraction. 
The rule based methods encompass most of the 
previous models. The statistical methods convert the extraction task into a token labeling 
task, identifying the target entities through the assignment of labels as in a typical 
Named Entity Recognition task. Traditionally, Hidden Markov Models \cite{Leek1997,Freitag1999}, 
Linear Chain Conditional Random Fields \cite{Lafferty2001}, and Maximum Entropy Taggers 
\cite{McCallum2000} have been the usual choice for linear sequence tagging models.
More recently, with the advancement of Natural Language Processing and Deep Learning, 
neural models outperformed previous NER methods for plain text. Huang et. al. \cite{Huang2015} introduced the 
bidirectional Long Short-Term Memory (LSTM) model with a Conditional Random Field (CRF) output layer
for NER. Ma and Hovy \cite{Ma2016} incorporated Convolutional Neural Network based character representations 
on top of the architecture. And Lample et. al. \cite{Lample2016} introduced
LSTM based character representations.

@@

Most data extraction systems focus on extracting information from single websites
and are therefore unsuited for cross website extraction tasks. Even unsupervised
approaches that are domain independent, such as RoadRunner \cite{Crescenzi2001} 
and EXALG \cite{Arasu2003} only work well for extracting data from pages generated 
from a same template.

A statistical approach to unsupervised domain 
independent web data extraction was described by Zhu et al \cite{Zhu2005}. The 2D CRF 
model takes a web page segmented into data blocks and employs a two dimensional conditional 
random field model to perform attribute labelling. The model was further improved
\cite{Zhu2006} to model record segmentation and attribute labelling as a joint task.
Some of the limitations of early unsupervised methods 
were also tackled by ObjectRunner \cite{Abdessalem2010} and AMBER \cite{Furche2012}. 
These methods work by annotating webpages automatically with regular expressions, gazetteers and 
knowledge bases. They can rectify low quality annotations and even improve the annotators
by exploring regular structures in the DOM during the record segmentation phase.

Web data extraction methods have undoubtedly improved extraordinarily, but
as pointed by Schulz et al. \cite{Schulz2016}, it is difficult to compare the results 
achieved by competing tools, and many seem to rely excessively on heuristic methods.
In that regard, the recent advancements in sequence taggers may provide more robust and
flexible extraction tools.

@@

Many web data extraction systems rely on hand crafted rules or gazetteers to perform
attribute annotation. Machine learning approaches to NER can improve annotations of 
more complex entities and even perform entity detection without any feature
engineering. We explored many methods of Named Entity Recognition
in the context of a web data extraction task. First, we discuss two traditional 
approaches: Hidden Markov Models, and Linear Chain Conditional Random Fields. Then,
we explore neural network architectures.

@@

Since $ P(X) $ is the same for all label sequences $ Y $, we can simply maximize
the probability $ P(X|Y) P(Y) $.

A HMM makes two assumptions. First, the probability of being in a given state depends 
only on a fixed number of previous states. That is:

\begin{equation}
P(y_i|y_{i-1}x_{i-1}, y_{i-2}x_{i-2}, ..., y_1x_1) = P(y_i|y_{i-1}, y_{i-2},..., y_{i-k})
\end{equation}

In fact, we can get much better results on the NER task by looking at trigrams
or quadrigrams ($ k = 2 $ or $ k = 3 $) instead of bigrams as a regular HMM. 
Some label assignments are highly improbable, such as single token named entities 
separated by a common word. These kinds of patterns can be perceived by a higher order HMM.
Second, the probability of a word depends only on its assigned label. That is:

\begin{equation}
P(x_i|y_{i-1}x_{i-1}, ..., y_1x_1) = P(x_i|y_i)
\end{equation}

With these assumptions, 
the probability $ P(Y|X) $ can be approximated by the expression:

@@

All relevant probabilities can be estimated through maximum likelihood estimation from the relative
frequencies of labels and features in the corpus. The best sequence of labels can be computed 
with a variable state Viterbi approach \cite{Li2000}. However, as we increase $ k $, this computation 
becomes exponentially more expensive. The beam-search strategy may be employed for a faster 
search, but we found that for $ k \leq 4 $, the Viterbi algorithm is still viable.

HMM based taggers have been succesfully applied in many NLP and WDE tasks 
\cite{Rabiner1990,Leek1997,Freitag2000}. They are incredibly fast to train and also they are very 
interpretable, making them a good choice for a first approximation. However, these models 
are highly dependent on the right selection of features, what may outweigh the benefit of a 
small training cost.

@@

In the task of NER on HTML, there are useful features related to the HTML
structure that can help in identifying named entities. On a given website, named
entities tend to occur inside the same HTML tags. The HTML tag feature or other
HTML features could easily be incorporated in the HMM. However, these 
features are only useful inside a single website and they cannot be generalized, 
because different websites use distinct HTML templates. 
Therefore, we propose a self training strategy to obtain probabilities for
these HTML features. It is implemented like this:

\begin{itemize}
\item Train the HMM without any HTML features.
\item Compute labels for a website with the trained HMM.
\item Use the computed labels as a proxy for the actual labels in the 
website and estimate HTML feature frequencies for this website alone.
\item Recompute the labels now using the HTML feature probabilities.
\end{itemize}

In theory, this strategy could be used with any sequence tagger, however
retraining a classifier with new features can become prohibitively expensive.
This strategy is only possible because the computation of HTML feature
frequencies can be performed very quickly. This adds very little overhead 
to the original HMM and improves precision and recall by a considerable 
margin.

@@

which is a sum over all possible label assignments $ Y $. The partition function can be efficiently
and exactly calculated with the sum-product algorithm. Parameter estimation is usually done through 
negative log likelihood minimization. The function can be optimized with techniques suitable for other 
maximum entropy models such as L-BFGS \cite{Liu1989}. The most likely label sequences can be decoded 
with the Viterbi algorithm, as was the case for HMMs.

CRFs are more general than HMMs because the transitions from $ y_{t-1} $ to $ y_{t} $ can depend 
on the whole vector of observations $ X $. This flexibility of feature functions allows for a wide range of
possibilities. Recently, CRFs have been succesfully employed as the output layer in complex neural 
architectures bringing improvements over models that compute labels independently.

\subsection{Neural Network Architectures}

\begin{figure}
  \centering
  % \includegraphics[width=0.5\textwidth]{pics/rnn_network}
  \includegraphics[width=400px]{pics/rnn_network}
  \caption{RNN for NER}
  \label{fig:rnn_network}
\end{figure}

@@

Although RNNs are theoretically capable of learning long term dependencies, in practice 
it becomes difficult due to vanishing gradients. Long short term memory networks (LSTM) were 
introduced by Hochreiter and Schmidhuber \cite{Hochreiter1997} with this problem in mind and 
they have been popularized since then. LSTM cell implementations vary slightly in the literature.
Our implementation has the following definition:

@@

In NER related tasks, both past and future words are important when deciding the
label at time $ t $, but a regular LSTM network only takes past features into consideration. 
A bidirectional LSTM solves this problem by stacking two regular LSTMs, and feeding
them with observations in opposite directions. The first LSTM receives the forward
states and the second LSTM receives the backward states. The hidden states from both 
networks can be concatenated at each time step to produce the output label. With this 
architecture, Bidirectional LSTMs have information from all input features in the sequence at 
any given timestep.

@@

The unaccented lowercase token was used as the key for the Glove-100 embedding lookup.
A gazetteer was constructed from a researcher list extracted from DBLP with 1,595,771
names. Table \ref{tab:gazetteer} shows the precision, recall and F1 score obtained with an
exact gazetteer matching strategy in each data file as a baseline.
Feature 2 represents an exact match of a sequence of tokens to any of the 1,595,771 
names, and feature 3 represents a partial match. Feature 4 is the rounded logarithm of 
the frequency of a token in the gazetteer, and feature 5 is the rounded logarithm of the frequency
of a token in a word corpus obtained through a random crawl on university websites.
Features 6 to 11 represent a simple regular expression match to an email, number, 
honorific, URL, capitalization and punctuation sign.

Feature 12 represents the HTML enclosing tag and its parent concatenated. Feature 13
represents all CSS classes concatenated. These features are not very useful in a general
sense, because every HTML document has a different format, so only because a named entity
occurs inside a given HTML tag in a document we cannot say it is more likely to be the case 
in other documents. However, these features can be trained with the self-training strategy 
for HMMs described in section \ref{sssec:self_training}.

@@

Two experiments were conducted to evaluate the best models for named entity recognition
on HTML in the context of web data extraction. In the first experiment, we trained the NER models
using the entire training set (85 documents). In the second experiment, the training set was 
split into five non overlapping sets with 17 documents, and every model was trained
and tested once using each set, while the test data was kept unchanged. We wanted to verify 
how the models behaved when training data is limited, since labelling NER datasets can be a
very time consuming effort.

@@

% \bibliographystyle{unsrt}
% \bibliography{bibfile}

\begin{thebibliography}{}
  \bibitem[\protect\citename{Akmajian and Lehrer }1976]{Crescenzi2001}
   Akmajian, A. and Lehrer, A. (1976) NP-like quantifiers and the
   problem of determining the head of an NP. {\it Linguistic
   Analysis\/} {\bf 2}: 295--313.
  \bibitem[\protect\citename{Akmajian and Lehrer }1976]{Arasu2003}
   Akmajian, A. and Lehrer, A. (1976) NP-like quantifiers and the
   problem of determining the head of an NP. {\it Linguistic
   Analysis\/} {\bf 2}: 295--313.
\end{thebibliography}
